%\documentclass{report}

\begin{document}
    \section{Group Basics}
    
    \subsection{Groups}
    
    The first thing we would encounter in abstract algebra is a group... but you already encountered it. Refer to the chapter "Algebraic Structures" for the definition of a group and an abelian group.
    
    If the context is obvious, we will skip $\cdot$ and write $ab$ instead of $a \cdot b$. The identity of a group will be denoted $e$ or $1$.
    
    $G$ will always denote group in this chapter, unless stated otherwise.
    
    \begin{defn} \label{def_group_power}
        The product of $n$ occurrences of $x$ is denoted $x^n$. The product of $n$ occurrences of $x^{-1}$ is denoted $x^{-n}$. Also $x^0 = 1$.
    \end{defn}
    
    \begin{prop} \label{prop_group_basics}
        If $a,b,c \in G$, then \begin{enumerate}
            \item the identity of $G$ is unique.
            \item the inverse $a^{-1}$ is unique.
            \item $(a^{-1})^{-1}=a$.
            \item $(ab)^{-1} = b^{-1}a^{-1}$.
            \item if $ab=ac$, then $b=c$. Also, if $ba=ca$, then $b=c$.
            \item For $n,m \in \mathbb{Z}$, $x^nx^m = x^{n+m}$ and $(x^n)^{-1} = x^{-n}.$
        \end{enumerate}
    \end{prop}
    
    \begin{proof}
        \begin{enumerate} \item[]
        \item Let $e_1$ and $e_2$ be the identities of $G$. Then $e_1e_2=e_2e_1=e_1$, and $e_2e_1=e_1e_2=e_2$, from the definition of the identity. Therefore $e_1=e_2$.
        \item Let $b_1$ and $b_2$ the inverses of $a$. Then $b_1 = b_1(ab_2) = (b_1a)b_2 = b_2$.
        \item The definition of an inverse shows that $a$ is an inverse of $a^{-1}$. From (ii), such an inverse is unique.
        \item $(ab)b^{-1}a^{-1} = a(bb^{-1})a^{-1} = aa^{-1} = e$. Similarly $b^{-1}a^{-1}(ab) = e$. From (ii), the inverse of $ab$ is unique.
        \item $ab=ac \implies a^{-1}ab=a^{-1}ac \implies b=c$. Similar argument for $ba=ca$.
        \item TODO
        \end{enumerate}
    \end{proof}
    
    \begin{defn} \label{def_group_misc} \begin{itemize}
        \item[]
        \item $a,b \in G$ \emph{commute} if $ab=ba$.
        \item The \emph{order} of $x \in G$, denoted $|x|$, is the smallest positive integer $n$ such that $x^n=1$. If no such $n$ exists, then $|x|=\infty$.
        \item The \emph{order} of $G$, denoted $|G|$, is the cardinality of $G$ as a set.
    \end{itemize} \end{defn}
    
    \begin{defn} \label{def_group_example} \begin{itemize}
        \item[]
        \item TODO: Z/nZ
        \item TODO: Sn
    \end{itemize} \end{defn}
    
    \subsection{Isomorphism}
    
    Now, we want to tell whether two groups are "same," in the sense that there is a bijection between them preserving the relations.
    
    \begin{defn}[Homomorphisms and Isomorphisms] \label{def_group_homomorphism}
        Let $(G,\star)$, $(H,\diamond)$ be two groups. Then a map $\varphi: G \to H$ is a \emph{homomorphism} if for all $x,y \in G$, $\varphi(x \star y)=\varphi(x) \diamond \varphi(y)$. An \emph{isomorphism} is a bijective homomorphism. If there is an isomorphism between $G$ and $H$, we say they are \emph{isomorphic} and denote $G \cong H$.
    \end{defn}
    
    We may skip $\star$ and $\diamond$ here too if the context is clear, but you have to understand which operations are used at each positions.
    
    \begin{thm} \label{thm_isomorphic_groups}
        If $(G,\star)$ and $(H,\diamond)$ are isomorphic, with the isomorphism $\varphi$, then \begin{enumerate}
            \item $|G| = |H|$.
            \item $G$ is abelian iff $H$ is abelian.
            \item For any $x \in G$, $|x| = |\varphi(x)|$.
        \end{enumerate}
    \end{thm}
    
    \begin{proof}
    (1) $\varphi$ is bijective.
    
    (2) Suppose $G$ is abelian. Take $c,d \in H$. Since $\varphi$ is surjective, there are $a,b \in G$ such that $\varphi(a) = c$ and $\varphi(b) = d$. Then $cd = \varphi(a)\varphi(b) = \varphi(ab) = \varphi(ba) = \varphi(b)\varphi(a) = dc$. Therefore $H$ is abelian.
    
    Suppose $H$ is abelian. Take $a,b \in G$. Then $\varphi(ab) = \varphi(a)\varphi(b) = \varphi(b)\varphi(a) = \varphi(ba)$. Since $\varphi$ is injective, $ab = ba$. Therefore $G$ is abelian.
    
    (3) TODO
    \end{proof}
    
    \subsection{Group Actions}
    
    \begin{defn}[Group Action] \label{def_group_action}
        A \emph{group action} of $G$ on a set $A$ is a map $G \times A \to A$, mapping $g \times a$ to $g \cdot a$, such that for all $g_1,g_2 \in G$ and $a \in A$, \begin{enumerate}
            \item $g_1 \cdot (g_2 \cdot a) = (g_1g_2) \cdot a$, and
            \item $1 \cdot a = a$.
        \end{enumerate}
        We say that $G$ \emph{acts} on $A$.
    \end{defn}
    
    Again, we may skip $\cdot$.
    
    TODO: permutation representation
    
    \subsection{Subgroups}
    
    \begin{defn}[Subgroups] \label{def_subgroup}
        A subset $H$ of $G$ is a \emph{subgroup} of $G$ if $H$ is nonempty, and for all $x,y \in H$, we have $xy \in H$ and $x^{-1} \in H$. We denote $H \leq G$.
    \end{defn}
    
    A subgroup is also a group. To see why, there is an element $x$ in $H$ since $H$ is nonempty, then $x^{-1} \in H$, and finally $x x^{-1} = 1 \in H$.
    
    \begin{prop}[The Subgroup Criterion] \label{prop_subgroup_criterion}
        A subset $H$ of $G$ is a subgroup if and only if $H$ is nonempty and for all $x,y \in H$, $x y^{-1} \in H$. Also, a finite subset $H$ is a subgroup if and only if $H$ is nonempty and closed under multiplication.
    \end{prop}
    
    \begin{proof}
        $(\Rightarrow)$ Trivial.
        
        $(\Leftarrow)$ Since $H$ is nonempty, take an element $x \in H$. Then $x x^{-1} = 1 \in H$. This gives $1 x^{-1} = x^{-1} \in H$. Finally, $x (y^{-1})^{-1} = xy \in H$ since $y^{-1} \in H$.
        
        If $H$ is finite, then $|x|=n<\infty$. Therefore $x^{-1} = x^{n-1}$. Now we can use the first part of this proposition.
    \end{proof}
    
    %\begin{defn} \label{def_centralizer}
        %Assume $A$ is a nonempty subset of $G$. \begin{itemize}
            %\item The \emph{centralizer} of $A$ in $G$ is $C_G(A) = \{g \in G | gag^{-1}=a \quad \forall a \in A\}$.
            %\item The \emph{center} of $G$ is $Z(G) = \{g %\in G | gxg^{-1}=x \quad \forall x \in G\}$.
            %\item The \emph{normalizer} of $A$ in $G$ is %$N_G(A) = \{g \in G | gAg^{-1}=A\}$.
    %\end{itemize} \end{defn}
    %TODO: stabilizers, kernels. But should we really talk about this here in the first place?
    
    \subsection{Cyclic Groups}
    
    \begin{defn}[Cyclic Group] \label{def_cyclic_group}
        $G$ is \emph{cyclic} if $G = \{x^n | n \in \mathbb{Z}\}$ for some $x \in G$. For such $x$, we denote $G = \langle x \rangle$ and say $x$ is a \emph{generator} of $G$.
    \end{defn}
    
    \begin{prop} \label{prop_cyclic_group_order}
        $| \langle x \rangle | = |x|$ in $\langle x \rangle$. (These values can be infinite.)
    \end{prop}
    
    \begin{proof}
        TODO. Isn't it, like, trivial?? Right??
    \end{proof}
    
    \begin{thm} \label{thm_cyclic_isomorphic}
        Any two cyclic groups with the same order are isomorphic.
    \end{thm}
    
    \begin{proof}
        Suppose $| \langle x \rangle | = | \langle y \rangle | = n < \infty$. We will show that $\varphi: \langle x \rangle \to \langle y \rangle$ defined by $\varphi (x^k) = y^k$ is well-defined and an isomorphism.
        
        Suppose $x^a = x^b$. Then $x^{a-b} = 1$, and so $n | (a-b)$. Therefore $\varphi (x^a) = y^a = y^b = \varphi (x^b)$. This shows that $\varphi$ is well-defined.
        
        Next, $\varphi$ is clearly a homomorphism and a surjection. Since the two groups are finite, $\varphi$ is a bijection. Therefore $\varphi$ is an isomorphism.
        
        Next, if $| \langle x \rangle | = \infty$, then $\varphi: \mathbb{Z} \to \langle x \rangle$ defined by $\varphi (n) = x^n$ is an isomorphism.
    \end{proof}

\end{document}